\newpage
\section{Definition of Done}
In this section we will define when something is done. We will discuss when a backlog item is done, when sprints are done and when the final release is done.
\subsection{Backlog items}
A backlog item is done when it is 65\% tested. We decided on 65\% because 100\% testing is impossible and also testing in GOAL is very hard. It is better to use user tests, by running the game with the bot then testing it via GOAL-tests. We wanted more then 50\%, but we didn't want to set the minimum too high. That is why we decided on 65\% test coverage by GOAL-test.  Also a backlog item needs to be checked by all members, and everyone should agree that this item is implemented correctly. All test should pass and the code should be merged to the master branch.
\subsection{Sprints}
A Sprint is done when the features that should be tackled during this sprints are done. If a feature isn't done, the reason should be clear and it should be discussed with all team members that this feature is moved towards a next sprint. There should be a reflection about the sprint and we should contact the TA's. Problems during the sprints need to be discussed and a solution should be found. These solutions should be used for all upcoming sprints.
\subsection{Final release}
The final release is done, when all items stated in section must haves are implemented and at least 65\% tested. We choose again 65\% because, if all backlog items need to be at least tested for 65\% also the final product should be tested for at least 65\%. Also most items mentioned in section 2.1 should be implemented and tested. \newline
The product owner should see multiple demos. These demos are mentioned in the roadmap in section 2.2. The product owner should also agree with the final product. \newline
The product vision, product plan and the architectural design should be finished and delivered. Also the final report should be done and delivered. 

\newpage