\section{Product Backlog}
In this section we will describe some user stories and an initial release plan.

\subsection{User stories}
In this section we will describe some user stories. Each user story describes what the stakeholder should do in a certain situation. The user stories are put in order, so the highest priority is first.
\subsubsection{User stories of features}
As a public service management bot\\
I want to buy land\\
So that I can build stuff\\
\\
As a public service management bot\\
I want to build a convenience store on ground that I own\\
So that the indicator for the convenience store will go up.\\
\\
As a public service management bot\\
I want to build a terrace on ground that I own\\
So that the indicator for the terraces will go up.\\
\\
As a public service management bot\\
I want to demolish a building that I own\\
So that I can use the ground for other things\\
\\
As a public service management bot\\
If the game crashes\\
I want to stop running\\
So that I don't mess things up.\\
\\
As a public service management bot\\
I want to sell land\\
So that I have more money\\
\\
As a public service management bot\\
I want to be notified if houses are demolished\\
So that I can decide if I want to build something near there or not\\
\\
As a public service management bot\\
I want to understand the used language between stakeholders\\
So that I can communicate with other bot stakeholders.\\
\\


\subsubsection{User stories of know-how acquisition}
As a programmer\\
I need to learn the newest GOAL code\\
So we can build a GOAL-bot.\\
\\
As a programmer\\
I need to learn how to play the Tygron game\\
So we know how a bot should play it.\\
\\
As a programmer\\
I need to make a Tygron scenario\\
So we have a scenario the bot can play in.\\

\subsection{Initial release plan }
In this section we will describe an initial release plan. Per week there will be a list of what to release.

\subsubsection{Week 2}
In this week we will release a draft versions of the product vision document, the product plan document and the architectural design document.

\subsubsection{Week 3}
In this week we will release the final versions of the product vision document and the product plan document. We will also release the final scenario where our stakeholder should play in.

\subsubsection{Week 4}
In this week we will release a bot who is able to buy and sell land. Also it should be able to demolish land and buildings.

\subsubsection{Week 5}
In this week we will release a bot who is able to build in order to increase the score of its indicators. Also is should be able to keep track of its bank account and make sure it doesn't go bankrupt.

\subsubsection{Week 6}
In this week we will release a bot who is able to keep track of the decisions made by other stakeholders during the game.

\subsubsection{Week 7}
In this week we will release a bot who is able to decide which land is the best for building a certain building.

\subsubsection{Week 8}
In this week we will release a bot who is able to finish its goals.

\subsubsection{Week 9}
In this week we will release the final bot with all documentations.
\newpage
