\section{Outlook}
Next time we work on this project, we will focus on implementing the strategy. The complete strategy we want to have is described in appendix A. All this is not yet implemented in our bot, because we didn't have enough time to implement the connector and the bot. So next time, we would start implementing this. We would like to have more interaction with the other stakeholders. Also we would like the connector to have more percepts based on our strategy. So we start with implementing the strategy and when we think we need a more specific percept, we would implement this is the connector. Instead of implementing things in the connector and then looking at the strategy. Because we have the basic implementation this is now possible.

On a more general level we have also learned a lot. The most important of these is the importance of communication within a large software project. In the beginning the communication was net very well, and there were a lot of different ideas between us and the different stakeholders. But over this weeks that improved greatly. This was mostly because we underestimated the importance of it. It was the reason for a lot of conflicts and it felt somewhat as if we working against each other instead of with each other. But as stated over time this improved and thanks to a lot of communication we succeeded in working together very well.

Another thing that we should improve on is being on time. Although most of the time everyone was on time, there were also more than a few instances when people were more than the agreeable fifteen minutes late. We had not decided on any consequences for those cases. What we have learned however, is that if you do not decide on consequences for bad actions, the bad actions will continue. Even something simple like bring cake the next time if you are late would help to decrease the frequency of such bad actions.