\section{Introduction}

This document provides a sketch of the system that is going to be built during the context project Virtual Humans. The architecture of the system is explained in the form of high level components of the system. These components are split in to sub components and sub-systems. This document will be continuously updated during the project development.

\subsection{Design goals}
During the development process we define certain goals the project should reach, next to solving the original problem. The following design goals will be maintained throughout the project:

\subsubsection{Availability}
The system will be built by the principle of Scrum, meaning that each week a working version is available for testing. By doing this we ensure that we are building what the clients wants; if (s)he sees features (s)he does not like we remove them, if they have other requirements we add them. 

\subsubsection{Manageability}
The bot is able to be turned off and on. Its property can be managed (including its money). The goals can be altered to a higher demand.

\subsubsection{Performance}
It should not be easily noticed that the bot is not a human due to slow functioning of the bot.

\subsubsection{Reliability}
The bot should work in any given scenario, although it might decide it is better to do nothing.

\subsubsection{Scalability}
Our bot will be able to work together with other bots and in theory an infinite amount could be added. In a practical sense if an infinite amount would be added, an error would occur more likely with the tygron engine than with our bot.

\newpage